### 2017-09-23 src/1_Introduction.tex
cambio intro
Solo falta relacion con los objetivos en capitulo de conclusiones

Models effectiveness were focused on the out-of-sample forecast rather than on the in-sample fitting. This criteria allows the OVECM and AVECM prediction capability to be expressed rather than just explaining data history. Our method performance is compared with its optimal offline algorithm.

@@

Vector error correction model (VECM) introduces this long-run relationship
among a set of cointegrated variables as an error correction term. VECM is a
special case of the vector autoregresive model (VAR) model. VAR model
expresses future values as a linear combination of variables past values.
However, VAR model cannot be used with non-stationary variables. VECM is a
linear model but in terms of variable differences. If cointegration exists,
variable differences are stationary and they introduce an error correction term
which adjusts coefficients to bring the variables back to equilibrium. In
finance, many economic time series turn to be stationary when they are
differentiated and cointegration restrictions often improves
forecasting~\cite{duy1998}. Therefore, VECM has been widely adopted.

@@

Chapter 1 contains relevant finance concepts required to understand financial
time series models such as market hypothesis, frequency, order book generation,
market microstructure.
Chapter 2 discuss main time series models including classic ones such as ARMA,
GARCH and more recent ones such as VECM, VAR and volatility models. %mejorar
Chapter 3 gives a brief introduction to machine learning and its variant online
learning. 
Chapter 4 presents different algorithms propose to forecast financial time
series using machine learning techniques.
In Chapter 5 a deep study of foreign exchange market features is presented and
experiments of cointegration are carried out in order to show its dynamic.
Chapter 6 presents a discussion of found results and summarise the main
conclusions of this thesis. It also presents some research directions for future
studied.

>>>>

Models effectiveness were focused on the out-of-sample forecast rather than on
the in-sample fitting. This criteria allows the OVECM and AVECM prediction
capability to be expressed rather than just explaining data history. Our method
performance is compared with the naive forecast of the random walk model and
ARIMA which are the most widely used algorithms for modelling a multivariate
time series.

@@

Vector error correction model (VECM) introduces this long-run relationship
among a set of cointegrated variables as an error correction term. VAR model
expresses future values as a linear combination of variables past values.
However, VAR model cannot be used with non-stationary variables. VECM is a
linear model but in terms of variable differences. If cointegration exists,
variable differences are stationary and they introduce an error correction term
which adjusts coefficients to bring the variables back to equilibrium. In
finance, many economic time series turn to be stationary when they are
differentiated and cointegration restrictions often improves
forecasting~\cite{duy1998}. Therefore, VECM has been widely adopted.

@@

Chapter \ref{chapter:HFT} contains relevant finance concepts required to understand financial
time series models such as market hypothesis, frequency, order book generation,
market microstructure.
Chapter \ref{chapter:FTT} discuss main characteristics and concepts of financial
time series including classic models such as ARMA, ARIMA,
GARCH and more recent ones such as VECM, VAR and volatility models.
Chapter \ref{chapter:MLM} gives an introduction to machine learning and its
variant online learning. 
Chapter \ref{chapter:proposal1} presents the first proposal called AVECM which
includes a new parallel method to choose VECM parameters based on the maximisation of the
percentage of cointegration.
In Chapter \ref{chapter:proposal2} a second approach is presented called OVECM,
which is an online version of OVECM for high frequency data.
Chapter \ref{chapter:conclusions} presents a discussion of found results and summarise the main
conclusions of this thesis. It also presents some research directions for future
study.

### 2017-09-23 src/5_1_Proposal.tex
Solo falta relacion con los objetivos en capitulo de conclusiones

Before running the tests, we firstly checked whether the time series were I(1)
using the Augmented Dickey Fuller (ADF) test with lags $p=1,2,3,4,5$.
\cite{mackinnon2010} presented critical values for rejection of hypothesis of a
unit root: -2.62 (1\%), 1.94 (5\%) and 1.62 (10\%).
\begin{table*}[ht]
\label{tab:adf}
\centering
\begin{tabular}{llllll}
\toprule
{Variable} & {ADF(1)} & {ADF(2)} & {ADF(3)} & {ADF(4)} & {ADF(5)}\\ 
\midrule
EURUSD &  -0.052   & -0.054  & -0.054  & -0.054  & -0.054  \\
GBPUSD &  -0.744  & -0.784  & -0.805  & -0.837  & -0.846  \\
USDCHF &  -0.476   & -0.493  & -0.493  & -0.495  & -0.502  \\
USDJPY &  0.357   & 0.360  & 0.360  & 0.367  & 0.367  \\
$\Delta$ EURUSD & -128.4*  & -128.4*  & -96.85* & -89.12*   & -89.12*\\
$\Delta$ GBPUSD & -131.4*  & -112.7*  & -102.5* & -92.86*   & -88.29*\\
$\Delta$ USDCHF & -127.8*  & -127.8*  & -96.94* & -88.82*   & -80.79*\\
$\Delta$ USDJPY & -135.1*  & -135.1*  & -101.2* & -101.2*   & -101.2*\\
\bottomrule
\addlinespace[1ex]
\multicolumn{6}{l}{ \textsuperscript{*} Indicates significance at 1\% level} \\
\multicolumn{6}{l}{ \textsuperscript{**} Indicates significance at 5\% level} \\
\multicolumn{6}{l}{ \textsuperscript{***} Indicates significance at 10\% level} \\
\multicolumn{6}{l}{MacKinnon critical values for rejection of hypothesis of a unit root are:}\\
\multicolumn{6}{l}{ -2.62 (1\%), -1.94 (5\%) and -1.62 (10\%)}\\
\multicolumn{6}{l}{ADF($d$) Augmented Dickey-Fuller test with lag $d$} 
\end{tabular}
\caption{Unit roots tests for EURUSD, GBPUSD, USDCHF and USDJPY at 10-second
frequency.}
\end{table*}
Table~\ref{tab:adf} shows that all currency rates cannot reject the unit root
test in their level form considering different lags, but they rejected it with
their first differences. This means that all of them are I(1) time series and we
are allowed to use VECM and therefore our proposed AVECM.

>>>>

Before running the tests, we firstly checked whether the time series were I(1)
using the Augmented Dickey Fuller (ADF) test with lags $p=1,2,3,4,5$.
\cite{mackinnon2010} presented critical values for rejection of hypothesis of a
unit root: -2.62 (1\%), 1.94 (5\%) and 1.62 (10\%).
Table \ref{tab:adf} shows that all currency rates cannot reject the unit root
test in their level form considering different lags, but they rejected it with
their first differences. This means that all of them are I(1) time series and we
are allowed to use VECM and therefore our proposed AVECM.
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
\toprule
{Variable} & {ADF(1)} & {ADF(2)} & {ADF(3)} & {ADF(4)} & {ADF(5)}\\ 
\midrule
EURUSD &  -0.052   & -0.054  & -0.054  & -0.054  & -0.054  \\
GBPUSD &  -0.744  & -0.784  & -0.805  & -0.837  & -0.846  \\
USDCHF &  -0.476   & -0.493  & -0.493  & -0.495  & -0.502  \\
USDJPY &  0.357   & 0.360  & 0.360  & 0.367  & 0.367  \\
$\Delta$ EURUSD & -128.4*  & -128.4*  & -96.85* & -89.12*   & -89.12*\\
$\Delta$ GBPUSD & -131.4*  & -112.7*  & -102.5* & -92.86*   & -88.29*\\
$\Delta$ USDCHF & -127.8*  & -127.8*  & -96.94* & -88.82*   & -80.79*\\
$\Delta$ USDJPY & -135.1*  & -135.1*  & -101.2* & -101.2*   & -101.2*\\
\bottomrule
\addlinespace[1ex]
\multicolumn{6}{l}{ \textsuperscript{*} Indicates significance at 1\% level} \\
\multicolumn{6}{l}{ \textsuperscript{**} Indicates significance at 5\% level} \\
\multicolumn{6}{l}{ \textsuperscript{***} Indicates significance at 10\% level} \\
\multicolumn{6}{l}{MacKinnon critical values for rejection of hypothesis of a unit root are:}\\
\multicolumn{6}{l}{ -2.62 (1\%), -1.94 (5\%) and -1.62 (10\%)}\\
\multicolumn{6}{l}{ADF($d$) Augmented Dickey-Fuller test with lag $d$} 
\end{tabular}
\caption{Unit roots tests for EURUSD, GBPUSD, USDCHF and USDJPY at 10-second
frequency.}
\label{tab:adf}
\end{table}
